---
title: "Image-To-RoutMap"
author: "venkata krishnan"
linkedIN: "https://www.linkedin.com/in/venkatakrishnanm/"
date: "January 4, 2018"
output: html_document
runtime: shiny
---
This R shiny application facilitates the user to dynamically plot a rout map using the image of the address. The imaged input is uploaded by the user is processed to create route maps. It facilitates the user to plan his journey by dynamically creating "N" number of route maps based on the user inputs. The route maps are created by computing the distance between the users origin and his various destinations and this distance information is also made available to the user. We use several packages for this application which are loaded initially.  
```{r}
library(shiny)
library(shinyFiles)
library(leaflet)
library(googleway)
library(tidyr)
library(ggmap)
library(gmapsdistance)
library(abbyyR)
library(shiny)
library(magick)
library(magrittr)
library(leaflet)
```
# Input
We have User interface and a server side for running the application the UI is used to gathers user inputs. The image inputs of the destination address are given as the input by browsing through the file in the system. As a sample we have facilitate to provide two image inputs.  

```{r setup, include=FALSE}
ui <- fluidPage(
  titlePanel('Use an image of your destination address for directions'),
  sidebarLayout(
    sidebarPanel(
      fileInput(inputId = 'files', 
                label = 'Upload the address of your destination as an image',
                multiple = FALSE,
                accept=c('image/png', 'image/jpeg')),
      fileInput(inputId = 'files2', 
                label = 'Upload the address of your destination as an images',
                multiple = FALSE,
                accept=c('image/png', 'image/jpeg')),
      "The Distance from the starting point are shown:",
      textOutput("txt"),
      textOutput("txt2"),
          submitButton("Submit")),
      imageOutput('images')),
    
    mainPanel(
      " Each time time you update your start address pls update the destination",
      textOutput('extracted'),
      leafletOutput("myma"),
      leafletOutput("myma1"),
      uiOutput('markdown')
    )
  )

```
# Computations
In the server sider internal computation is done to extract the text from the image inputs and google API is used to generate maps and to compute distance between the origin and the destinations. The first map is generated by taking the starting point of the user as as origin and the address which as nearest to the origin as the first destination, while the next map is generated by taking the first destination of the user as an origin point and so on.   
```{r eruption, echo=FALSE}

server<-function(input,output)
  {  
    output$files <- renderTable(input$files)
    
    files <- reactive({
      files <- input$files
      files$datapath <- gsub("\\\\", "/", files$datapath)
      files
    })
    
    data1<-reactive({
      if (is.null(input$files)) return(NULL)
      # Fix file path
      text <- image_read(files()$datapath[1]) %>%
        image_resize("2000") %>%
        image_convert(colorspace = 'gray') %>%
        image_trim() %>%
        image_ocr()
      text
    })
    
    output$files2 <- renderTable(input$files2)
    
    files2 <- reactive({
      files2 <- input$files2
      files2$datapath <- gsub("\\\\", "/", files2$datapath)
      files2
    })
    
    data12<-reactive({
      #if (is.null(input$files2)) return(NULL)
      # Fix file path
      text2 <- image_read(files2()$datapath[1]) %>%
        image_resize("2000") %>%
        image_convert(colorspace = 'gray') %>%
        image_trim() %>%
        image_ocr()
      text2
    })
    output$txt<-renderText({dis1<-mapdist(from = "5 Dolphin's Barn, Ushers, Dublin, D08", to = data1(),
                                          mode = "driving")
    dis1$km})
    output$txt2<-renderText({dis2<-mapdist(from = "5 Dolphin's Barn, Ushers, Dublin, D08", to = data12(),
                                           mode = "driving")
    dis2$km})
    
    data<-reactive({ 
      tr<-geocode(data1())
      tr2<-geocode(data12())
      to<-geocode("5 Dolphin's Barn, Ushers, Dublin, D08")
      
      arena_dist <- mapdist(from = "5 Dolphin's Barn, Ushers, Dublin, D08", to = data1(),
                            mode = "driving")
      arena_dist2 <- mapdist(from = "5 Dolphin's Barn, Ushers, Dublin, D08", to = data12(),
                             mode = "driving")
      dis1<-arena_dist$miles
      dis2<-arena_dist2$miles
      if(dis1 < dis2){
        des = c(tr$lat, tr$lon)
        rt<-as.data.frame(des)
      }else{
        des = c(tr2$lat, tr2$lon)
        rt<-as.data.frame(des)
      }

      res <- google_directions(origin = c(to$lat, to$lon),
                               destination = rt[c(1,2),],
                               key = "AIzaSyA9Otv6_W0Gr9vQibeepDKpqQOzSBVjKa0")
      df_polyline <- decode_pl(res$routes$overview_polyline$points)
      df_polyline
    })

    data5<-reactive({ 
      tr1<-geocode(data1())
      tr2<-geocode(data12())
      res <- google_directions(origin = c(tr1$lat, tr1$lon),
                               destination = c(tr2$lat,tr2$lon),
                               key = "AIzaSyA9Otv6_W0Gr9vQibeepDKpqQOzSBVjKa0")
      df_polyline <- decode_pl(res$routes$overview_polyline$points)
      df_polyline
      #     df_polyline
    }) 
    
    output$myma <- renderLeaflet( {       
      leaflet() %>%
        addTiles() %>%
        addPolylines(data = data(), lat = ~lat, lng = ~lon)
    })
    output$myma1 <- renderLeaflet( {       
      leaflet() %>%
        addTiles() %>%
        addPolylines(data = data5(), lat = ~lat, lng = ~lon)
    })
  }
shinyApp(ui = ui, server = server)
```

This application is built with an aim to help delivery person to work efficiently. As the application takes an imaged input no manual typing of the delivery address would be required and dynamic route maps based on several destination addresses are generated by computing the distances of each location from the origin. This facilitates the driver to have a planned route map of all their destinations with corresponding distance.
     

